Mergeable Types

### 2017-02-28 paper/mergeable-types.tex
edits
Added a note.

@@

\begin{definition} [\bfseries Mergeable Type]
\label{def:mergeable-type-2}
A type $t$ is said to be mergeable if and only if the following
conditions hold:
\begin{itemize}
  \item There exists a function $W: t \times t \rightarrow (t
  \rightarrow t)^*$ that accepts an object $A:t$ and its
  semantic successor $B:t$, and returns a minimal sequence of
  primitive morphisms $P^*$, whose composition maps $A$ to $B$. That
  is, $W(A,B) = P^*$, where $\denot{P^*}(A) = B$, and there does not
  exist an $R^*$ such that $\denot{R^*}(A) = B$ and $\length{R^*} <
  \length{P^*}$

@@

Def.~\ref{def:mergeable-type-2} is immediately applicable to the list
type, and lets us explain why it is a mergeable type.  \C{MList.edit\_seq}
and \C{MList.op\_transform}, respectively, are the evidences for the
existence of $W$ and $M$ functions.

>>>>

The proof follows directly from the fact that the values on branches
are computed from previous values either by applying morphisms
locally, or by merging from the remote branches. In the latter case,
Def.~\ref{def:mergeable-type} guarantees that the existence of a
morphism from the merging value to the merged value.

@@

\begin{definition} [\bfseries Mergeable Type (Strengthened)]
\label{def:mergeable-type-2}
A type $t$ is said to be mergeable if and only if the following
conditions hold:
\begin{itemize}
  \item There exists a function $W: t \times t \rightarrow (t
  \rightarrow t)^*$ that accepts an object $A:t$ and its
  semantic successor $B:t$, and returns a minimal sequence of
  primitive morphisms $P^*$, whose composition maps $A$ to $B$. That
  is, $W(A,B) = P^*$, where $\denot{P^*}(A) = B$, and there does not
  exist an $R^*$ such that $\denot{R^*}(A) = B$ and $\length{R^*} <
  \length{P^*}$

@@

Def.~\ref{def:mergeable-type-2} is immediately applicable to the list
type, and lets us explain why it is a mergeable type.  \C{MList.edit\_seq}
and \C{MList.op\_transform}, respectively, provide evidences for the
existence of $W$ and $M$.
